%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Charles Schwab} % Organization
    {Austin, TX} % Location
    {Jan 2018 - Present} % Dates(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a new single page client-facing web application on Schwab.com with accessibility in mind.}
        \item {Leading efforts to migrate our web application from a .NET Framework to .NET Core MVC application in order to best utilize Pivotal Cloud Foundry.}
        \item {Collaborated with service providers to harden REST services consumed by application for production environment.}
        \item {Utilized natural language processing toolkit to address security concerns and minimize client risk.}
        \item {Improved unit test code coverage of the web application from 40\% to 95\%.}
        \item {Exercised CI/CD by maintaining a team VM and testing environments.}
        \item {Developed internal tools to streamline Schwab developer on-boarding process. Reduced setup time by 80\% from a few weeks to two days and now a standard part of on-boarding procedure.}
        \item {Mentor other developers and interns by teaching coding standards and cultivating a collaborative culture.}
        \item {Technologies used: Angular, Typescript, C\#.NET, Jasmine, Atlassian Stack, Git}
      \end{cvitems}
    }
      
%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {CITI} % Organization
    {Irving, TX} % Location
    {Jun 2017 - Aug 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered load balancer information display onto Citi Automation Services (CAS) to ease management of VMs}
        \item {Created API for drill down option and load balancer display}
        \item {Technologies used: AngularJS, SQL, Git, Jenkins, Spring Tool Suite}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {NASA} % Organization
    {Houston, TX} % Location
    {Aug 2016 - Dec 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with a team of interns on development of a code coverage tool used for the Orion spacecraft flight software}
        \item {Developed a Python GUI that merges code coverage data with compatible files, using intelligent merging, from multiple tests based on certain metadata and displays the merged data in an HTML file}
        \item {Automated code coverage report file organization to simplify tool use}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {CITI} % Organization
    {Irving, TX} % Location
    {Jun 2016 - Aug 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered a web application to assist the testing integration team and application owners test their applications on several remote test machines}
        \item {Automated unit test execution to ensure expected performance on multiple operating systems and platforms}
        \item {Technologies used: ASP.NET and Javascript }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
